Bayesian Exploration with Unbiased History

### 2018-08-21 posterior.tex
Some change to posterior part

\begin{example}
Let the prior distribution be the uniform distribution over two Bernoulli distributions. Suppose there are $a$ 1's in $n$ samples. Then the posterior mean is $\frac{a+1}{n+2}$ and the empirical mean is $\frac{a}{n}$. Their difference is at most $\frac{1}{n+2}$. 
\end{example}

>>>>

\begin{example}
Let the prior distribution be the uniform distribution over Bernoulli distributions. Suppose there are $a$ 1's in $n$ samples. Then the posterior mean is $\frac{a+1}{n+2}$ and the empirical mean is $\frac{a}{n}$. Their difference is at most $\frac{1}{n+2}$. 
\end{example}

\begin{example}
Let the prior distribution be the uniform distribution over Bernoulli distributions with mean between $1/3$ and $2/3$. Suppose we have $n$ samples. With probability at least $\Omega(1/\sqrt{n})$, the difference between empirical mean and posterior mean is larger than $1/\sqrt{n}$.
\end{example}
